Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-17 awipev-CO2.Rmd
added as.POSIXct(...) for all datetime

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
d_all <
```

@@

# Add the flag location: some samples have been collected at the pier. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1, 0)
  )
d <- d%>%
  dplyr::filter(location_flag== 0)

@@

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= "2017-08-29 10:00:00")
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= "2017-08-24 19:00:00")
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "No data")
#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  #discrete_scale(labels = labels) + 
  coord_flip() +
  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  theme_bw()
p
rm(d)
```

@@

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
                temp_fb = ifelse(temp_fb >15, NA, temp_fb))

@@

```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
  #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="at_calc",color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  #dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

# set deployment period when seaFET is in/out of water
sfinterv <- c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00")

# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01,
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
                                ifelse(datetime >= sfinterv[3] , 03,NA ))))

@@

# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
# (2) removed from 2018-01-08 to 2018-02-02
# (3) outliers removed
# (1)
d_all$phINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT < 8.04, NA, d_all$phINT) 
d_all$phEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT < 8.04, NA, d_all$phEXT) 
d_all$voltINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltINT < -0.9439, NA, d_all$voltINT) 
d_all$voltEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
# (2)
d_all$voltINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltINT)
d_all$voltEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltEXT)
d_all$phINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT)
d_all$phEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT)
# (3)
d_all$voltINT <- ifelse(d_all$datetime == "2017-11-02 21:00:00" | d_all$datetime == "2018-04-18 14:00:00", NA, d_all$voltINT)

#periode 1, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltINT_4h, voltINT))

mean_voltEXT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltEXT_4h, voltEXT))

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_mix = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_mix))

# Periode 2, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))

mean_voltEXT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltEXT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltEXT_4h, voltEXT))

# period 03, mean of 4 previous hours for volt int + volt ext
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))

mean_voltEXT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltEXT_4h, voltEXT))

# period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))

mean_voltEXT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltEXT_4h, voltEXT))

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_mix = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_mix))

#interpolation of salinity during the FB off maintenance
salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
names(salinterp) <- c("datetime", "sal_mix_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_mix_interp <- salinterp$sal_mix_interp

d_all <- d_all %>%
  dplyr::mutate(sal_mix_interp =  ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-16 16:00:00", sal_mix_interp, sal_mix))

>>>>

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
#d_all <
```

@@

# Add the flag location: some samples have been collected at the pier. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == as.POSIXct("2016-04-21 09:25:00") | 
                                         datetime == as.POSIXct("2016-02-10 14:00:00") | 
                                         datetime == as.POSIXct("2016-02-17 09:20:00") |
                                         datetime == as.POSIXct("2016-02-24 14:20:00") |
                                         datetime == as.POSIXct("2016-02-04 09:30:00") |
                                         datetime == as.POSIXct("2016-01-27 15:00:00") |
                                         datetime == as.POSIXct("2016-01-13 13:45:00") |
                                         datetime == as.POSIXct("2016-01-06 14:10:00") |
                                         datetime == as.POSIXct("2015-12-24 10:45:00") |
                                         datetime == as.POSIXct("2015-12-30 13:30:00") |
                                         datetime == as.POSIXct("2018-01-05 15:20:00") |
                                         datetime == as.POSIXct("2018-02-02 14:35:00") |
                                         datetime == as.POSIXct("2018-03-02 14:10:00") |
                                         datetime == as.POSIXct("2019-05-31 11:45:00"), 
                                       1, 0))
d <- d %>%
  dplyr::filter(location_flag == 0)

@@

s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "No data")
#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
zz <- pivot_longer(z, -Flag)
p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  #scale_y_reverse() +
  #discrete_scale(labels = labels) + 
  coord_flip() +
  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  theme_bw()
p
rm(d)
```

@@

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(
    temp_fb = ifelse(
      datetime >= as.POSIXct("2017-03-22 08:00:00") &
        datetime <= as.POSIXct("2017-03-23 16:00:00"),
      NA,
      temp_fb
    ),
    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
  )
fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)

@@

```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
TAevents <- as.POSIXct(c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00",
              "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(),
              "%Y-%m-%d %H:%M:%S")))
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
  #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="at_calc",color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  #dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

# set deployment period when seaFET is in/out of water
sfinterv <- as.POSIXct(c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00"))

# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01,
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
                                ifelse(datetime >= sfinterv[3], 03, NA ))))

@@

# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
# (2) removed from 2018-01-08 to 2018-02-02
# (3) outliers removed
# (1)
d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                        d_all$datetime <= as.POSIXct("2018-01-08") &
                        d_all$phINT < 8.04, NA, d_all$phINT)
d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                       d_all$datetime <= as.POSIXct("2018-01-08") &
                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                         d_all$datetime <= as.POSIXct("2018-01-08") &
                         d_all$voltINT < -0.9439, NA, d_all$voltINT) 
d_all$voltEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
                         d_all$datetime <= as.POSIXct("2018-01-08") &
                         d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
# (2)
d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"), 
                        NA, d_all$voltINT)
d_all$voltEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                        NA, d_all$voltEXT)
d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                      NA, d_all$phINT)
d_all$phEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
                      NA, d_all$phEXT)
# (3)
d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
                          d_all$datetime == as.POSIXct("2018-04-18 14:00:00"),
                        NA, d_all$voltINT)
#periode 1, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
mean_voltEXT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  ) %>%
  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
mean_TseaF_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  ) %>%
  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))
# Periode 2, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
mean_voltEXT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-09-28 15:00:00") &
      datetime <= as.POSIXct("2017-09-28 18:00:00")
  ) %>%
  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-09-28 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# period 03, mean of 4 previous hours for volt int + volt ext
mean_voltINT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 08:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
mean_voltEXT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 04:00:00") &
      datetime <= as.POSIXct("2019-09-13 07:00:00")
  ) %>%
  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2019-09-13 08:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
mean_voltINT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
mean_voltEXT_4h <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2019-09-13 11:00:00") &
      datetime <= as.POSIXct("2019-09-13 12:00:00")
  ) %>%
  dplyr::summarise(mean(voltINT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2019-09-13 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
mean_TseaF_4h <- d_all %>%
